---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# deepdive

<!-- badges: start -->
<!-- badges: end -->

This package aims to provide simple intuitive functions to create quick protoypes of artificial neural network or deep learning models for general purpose application. In addition, check out experimental algorithms from my personal research , deeptree and deepforest for special cases to achieve better accuracy / generalisation.This github page will be updated for roadmap items and updates for improved fucntionalities and performance updates.

Feel free to reach me out at : rajeshbalakrishnan24@gmail.com for any suggestions and doubts or you can always leave a comment on github.

RoadMap:
1.Mini batch gradient descent for better performance
2.Parallelsation of deeptree and deepforest 
3.
## Installation

You can install the released version of deepdive from [GitHub](https://github.com/RajeshB24/deepdive) with:

``` r
devtools::install_github("RajeshB24/deepdive")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(deepdive)
## basic example code
 x <- data.frame(a = runif(1000)*100,
 b = runif(1000)*200,
 c = runif(1000)*100,
 d = runif(1000)*200)
 y<- data.frame(y=20*x$a +30* x$b+10*x$c +10)

 #train
 modelnet<-deepnet(x,y,c(2,2),activation = "relu",
 reluLeak = 0,
 modelType = "regress",
 iterations =4000,
 eta=0.8,
 optimiser="adam")

```

